\section{Experiment Design}
\label{sec:experiment}

\subsection{Research Questions}
\label{sec:questions}

(What defines influential changes? --- post-mortem metrics)

RQ0: What is the key metric to determine "influential changes" here?

(What makes influential changes?)

RQ1: Are complex changes influential in the future? (internal complexity 
---> size, cyclomatic, etc --- and inter-class+external complexity ---> class coupling, fan-in/out)

RQ2: Are early changes influential? (historical metrics)

RQ3: Do popular developer make influential changes? (social metrics)

(Why are influential changes important?)

RQ4: Do influential changes affect the popularity of projects? (profit/social impact)

RQ5: Do influential changes make developer influential? (social impact)

RQ6: Who does benefit from it?






\subsection{Subjects}

\dongsun{In this time, it seems we can only adopt Linux kernel. However, we can
list up sub-modules in the kernel.}



\subsection{Identifying Influential Changes}

\subsubsection{Metrics}
\label{sec:metrics}
We manually look into each commit detected by our post-mortem analysis program
and analyze the importance of this commit:

\begin{enumerate}
    \item Is it a fix to a long standing bug?
    \item Does it introduce a new feature or interface?
    \item Does it introduce a potential issue?
    \item Does it contain something that requires attention of other developers/users?
\end{enumerate}

\subsubsection{Experiment Procedure}
\label{sec:procedure}
For each project, we firstly collect its data, including source code repository
and issue reports with user comments in its issue tracking system. After
preprocessing we extract interesting artifacts and store them in a database
for reuse and query.  Then we try to find commits that could be influential
using different post-mortem metrics, such as how long an issue is resolved
since being reported and how long a file is updated since a previous commit and
remains unchanged until a next commit.  These commits are then undergone a
manual evaluation of whether it is influential or not and assigned a label
accordingly.

\input{04-model}


\subsection{Qualitative Analysis}

\dongsun{this section describes how we did qualitative analysis. For example,
how we sampled some of influential changes.}
